### 2018-05-05 papers/synth/intro.tex
asd

We have implemented the encoding in a flexible tool,
which can handle a wide range of synthesis query.
%
We have applied our tool on several VTSs including two found-in-nature
VTSs.
%
In figure~\ref{fig:mukund-vts}, we present one of the two for
mammalian cells obtained by studying the
literature.\footnote{Please read appendix~\ref{sec:ex-vts} for more biological details.}
%
The VTS has six nodes and 55 molecules.
%
We can easily check that stability condition is not satisfied for
many molecules for example ???.
%
On the example, our synthesis tool reports that minimum ?? edges needed
to be added to make the VTS stable.
%
The dashed edges are the suggested edges from our tool.
%
Our experiments suggest that the synthesis problems are
solvable by modern solvers and the synthesis technology may be useful
for biological research.
%
% We have also applied our tool on various synthetic examples to
% demonstrate that our tool scale upto the graph size size nodes, which
% is the size of typical VTSs in a eukaryotic cell.

>>>>

We have implemented the encoding in a flexible tool,
which can handle a wide range of synthesis query.
%
We have applied our tool on several VTSs including two found-in-nature
VTSs.
%
In figure~\ref{fig:mukund-vts}, we present one of the two for
mammalian cells obtained by studying the
literature.\footnote{Please read appendix~\ref{sec:ex-vts} for more biological details.}
%
The VTS has six nodes and 55 molecules.
%
We can easily check that stability condition is not satisfied for
many molecules for example ???.
%
On the example, our synthesis tool reports that minimum ?? edges needed
to be added to make the VTS stable.
%
The dashed edges are the suggested edges from our tool.
%
Our experiments suggest that some of the synthesis problems are
solvable by modern solvers and the synthesis technology may be useful
for biological research.
%
% We have also applied our tool on various synthetic examples to
% demonstrate that our tool scale upto the graph size size nodes, which
% is the size of typical VTSs in a eukaryotic cell.
